Sample size

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:bug: - fix package namespace

  sd_team <- purr::map(
    brm_model$model,
    ~tidybayes::spread_draws(.x, sd_team__Intercept) %>%
      dplyr::summarise(sd = sd(sd_team__Intercept)) %>%
      dplyr::pull()
  ) %>%
  unlist()

>>>>

  sd_team <- purrr::map(
    brm_model$model,
    ~tidybayes::spread_draws(.x, sd_team__Intercept) %>%
      dplyr::summarise(sd = sd(sd_team__Intercept)) %>%
      dplyr::pull()
  ) %>%
  unlist()
